---
title: "Anto Dasboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: [ "twitter", "facebook","whatsapp","instagram", "menu"]
---

```{r setup, include=FALSE}
library(flexdashboard)
library(knitr)
library(DT)
library(rpivotTable)
library(ggplot2)
library(plotly)
library(dplyr)
library(openintro)
library(highcharter)
library(tidyverse)
library(hrbrthemes)
library(kableExtra)
library(treemap)
```



```{r}
mydata <- read.csv("E:/ADI BUANA/LAST/data1.csv")
```

```{r}
mycolors <- c("blue", "#FFC125", "darkgreen", "darkorange")
```

Interactive Data Visualization
=====================================

Row
-------------------------------------

### Total unemployment

```{r}
valueBox(sum(mydata$pengangguran),
         icon = 'fa-area-chart')
```

### Highest poverty

```{r}
valueBox(max(mydata$penduduk_miskin),
         icon = 'fa-area-chart')
```

### Highest Illiterate

```{r}
valueBox(max(mydata$buta_huruf),
         icon = 'fa-area-chart')
```


Row
-------------------------------------

### Poverty By Province

```{r}
p1 <- mydata %>%
         group_by(provinsi) %>% 
         plot_ly(x = ~provinsi,
                 y = ~penduduk_miskin,
                 color = "red",
                 type = 'bar') %>%
layout(xaxis = list(title = " "),
yaxis = list(title = 'Percentage'))
p1
```



### Top poverty in Indonesia by Province

```{r}
p2 <- mydata %>%
         group_by(provinsi) %>%
         filter(penduduk_miskin>15) %>%
         plot_ly(labels = ~provinsi,
                 values = ~penduduk_miskin,
                 marker = list(colors = mycolors)) %>%
         add_pie(hole = 0.4) %>%
         layout(xaxis = list(zeroline = F,
                             showline = F,
                             showticklabels = F,
                             showgrid = F),
                yaxis = list(zeroline = F,
                             showline = F,
                             showticklabels=F,
                             showgrid=F))
p2
```


Row
-------------------------------------

### Illiterate in Indonesia by Province

```{r}
p3 <- mydata %>%
         group_by(provinsi) %>% 
         plot_ly(x = ~provinsi,
                 y = ~buta_huruf,
                 color = "green",
                 type = "bar") %>%
layout(xaxis = list(title = " "),
yaxis = list(title = 'Percentage'))
p3

```





###  Net Enrollment School

```{r}
p4 <- mydata %>%
         group_by(provinsi) %>% 
         plot_ly(x = ~provinsi,
                 y = ~partisipasi_sekolah,
                 color = "blue",
                 type = "bar") %>%
layout(xaxis = list(title = " "),
yaxis = list(title = 'Percentage'))
p4

```



###  Employment

```{r}
p5 <- mydata %>%
         group_by(provinsi) %>% 
         plot_ly(x = ~provinsi,
                 y = ~pengangguran,
                 color = "blue",
                 type = "bar") %>%
layout(xaxis = list(title = " "),
yaxis = list(title = 'Count'))
p5

```




Scatter Plot
=====================================

Row
-------------------------------------

### Scatter Plot of Poverty Vs Life Expectancy

```{r}
p6 <- plot_ly(mydata, x=~life_expentancy) %>%
         add_markers(y =~penduduk_miskin,
                     text = ~paste("Povery: ",penduduk_miskin),
                     showlegend = F) %>%
         add_lines(y = ~fitted(loess(penduduk_miskin ~ life_expentancy)),
                   name = "Loess Smoother",
                   color = I("#FFC125"),
                   showlegend = T,
                   line = list(width=5)) %>%
         layout(xaxis = list(title = "Life Expectancy"),
                yaxis = list(title = "Poverty"))
p6
```



### Scatter Plot of Poverty Vs Illiterate

```{r}
p7 <- plot_ly(mydata, x=~buta_huruf) %>%
         add_markers(y =~penduduk_miskin,
                     text = ~paste("Poverty",penduduk_miskin),
                     showlegend = F) %>%
         add_lines(y = ~fitted(loess(penduduk_miskin ~ buta_huruf)),
                   name = "Loess Smoother",
                   color = I("#FF0000"),
                   showlegend = T,
                   line = list(width=5)) %>%
         layout(xaxis = list(title = "Illiterate"),
                yaxis = list(title = "Poverty"))
p7
```


Row
-------------------------------------

### Scatter Plot of Poverty Vs Lama Sekolah

```{r}
p8 <- plot_ly(mydata, x =~ lama_sekolah) %>%
         add_markers(y =~penduduk_miskin,
                     text = ~paste("Poverty",penduduk_miskin),
                     showlegend = F) %>%
         add_lines(y = ~fitted(loess(penduduk_miskin ~ lama_sekolah)),
                   name = "Loess Smoother",
                   color = I("#E7298A"),
                   showlegend = T,
                   line = list(width=5)) %>%
         layout(xaxis = list(title = "Lama Sekolah"),
                yaxis = list(title = "Poverty"))
p8
```


### Scatter Plot of Poverty Vs Human development Index

```{r}
p9 <- plot_ly(mydata, x =~ ipm) %>%
         add_markers(y =~penduduk_miskin,
                     text = ~paste("Poverty",penduduk_miskin),
                     showlegend = F) %>%
         add_lines(y = ~fitted(loess(penduduk_miskin ~ ipm)),
                   name = "Loess Smoother",
                   color = I("#545454"),
                   showlegend = T,
                   line = list(width=5)) %>%
         layout(xaxis = list(title = "HDI"),
                yaxis = list(title = "Poverty"))
p9
```


Tree Map 
========================================

### Indonesia Poverty

```{r}
treemap(mydata,
          
          # data
          index="provinsi",
          vSize="penduduk_miskin",
          type="index",
          
          # Main
          title="",
          palette="Dark2",
          
          # Borders:
          border.col=c("black"),             
          border.lwds=1,                         
          
          # Labels
          fontsize.labels=0.5,
          fontcolor.labels="white",
          fontface.labels=1,            
          bg.labels=c("transparent"),              
          align.labels=c("left", "top"),                                  
          overlap.labels=0.5,
          inflate.labels=T                        # If true, labels are bigger when rectangle is bigger.
          
  )
  



```





Data Table
========================================

```{r}
datatable(mydata,
          caption = "Indonesia Poverty",
          rownames = T,
          filter = "top",
          options = list(pageLength = 5))
```



Summary {data-orientation=columns} 
===========================================

Column 
-----------------------------------

### Highest poverty

```{r}
valueBox(max(mydata$penduduk_miskin),
         icon = "fa-area-chart" )
```

### Lowest poverty


```{r}
valueBox(min(mydata$penduduk_miskin),
         icon = "fa-area-chart" )
```


### Highest Illiterate


```{r}
valueBox(max(mydata$buta_huruf),
         icon = "fa-area-chart" )
```


### Lowest Illiterate


```{r}
valueBox(min(mydata$buta_huruf),
         icon = "fa-area-chart" )
```

### Total Unemployment Indonesia
```{r}

valueBox(sum(mydata$pengangguran),
         icon = "fa-area-chart")
```


Column
---------------------------

Report

* The highest of poverty in Indonesia is Papua with  `r max(mydata$penduduk_miskin)` percent.

* The lowest poverty in Indonesia is DKI Jakarta with `r min(mydata$penduduk_miskin)` percect.

* The highest Illiterate in Indonesia is Papua with  `r max(mydata$buta_huruf)` percent.

* The lowest Illiter in Indonesia is DKI Jakarta with `r min(mydata$buta_huruf)` percent.

* The Total Unemployment in Indonesia  was `r sum(mydata$pengangguran)` million.

This report was generated on `r format(Sys.Date(), format = "%B %d, %Y")`.

About Report
========================================

Created by: Antonito HC (Majoring in Statistics and Minoring at Data Science & Business Analytics)
